% !TeX root = ../Tex/main.tex
\newpage
\subsection{Structure of the Paper}
\begin{enumerate}
    \item Introduction
        \begin{enumerate}
            \item I will copy and paste most of the parts of this research proposal. It seems to me like a good introduction.
            \item Brief intro to clarify some concepts to readers coming from economics: Safina's book, Safina's work/life, what are elephants and why do they matter
            \item The two examples (case 1 and case 2) from the book, (\textit{with proper citation})
            \item I will present the problem (\textit{thus the contradiction I believe I discovered}), along with a longer explanation of it. I will also draw a more precise connection with game theory, \textit{maybe I will use bullet points}
        \end{enumerate}
    \item Causal Inference \\ I will expand on the inference problem from more perspectives. I will clarify that the cognition of elephants is just an hypothesis, and I will state clearly this hypothesis. I will draw the DAG for the problem coming from biology. I will draw the DAG for the game theory problem I wish to describe, along with its assumptions.
    \item Models
        \begin{enumerate}
            \item Model n°1: perfect information and complete information for the case 1 from Safina's book
            \item Model n°2: perfect information and complete information for the case 2 from Safina's book
            \item Model n°3: According to what I come up with in the first part, I will try to put together a model that comprehends both of the two examples.
        \end{enumerate}
    \item Models on EGT
        \begin{enumerate}
            \item Introduction to EGT (\textit{history plus main concepts})
            \item Model n°4: Empathy is an ESS. With a good amount of luck I will by able to draw a model (\textit{maybe})
        \end{enumerate}
    \item Conclusion:\\I will make sure that from this part will not miss a general summary, a summary of the part coming from biology, a summary of the conclusions and of the resuls.
\end{enumerate}